Estimation of all-cause excess mortality by age-specific mortality patterns of COVID-19 pandemic in Peru in 2020

### 2021-03-21 article.Rmd
update

\begin{equation}
(\#eq:unreg)
   \begin{aligned}
  \widehat{\mu}_{\text{Deaths}_\text{Not reg}}= \big(1-\widehat{\text{Completeness}}\big)*
  \sum{\widehat{{\text{Excess}}_\text{Reg}}}
   \end{aligne*d}      
\end{equation}

@@

pander(t(a), caption = "(\\#tab:summary) Summary of estimations, Peru, 2020.", 
       style = 'rmarkdown', 
       split.table = Inf,
       round=1)

@@

``` {r map2, fig.cap="Age-standardised death rates"}

mr1<-ggplot() + geom_sf(data = DEPS,
                       aes(fill=adj.rate),size=.01,colour="white") +
  scale_fill_viridis_c( direction=1,option = "plasma",
                        name = "Mortality rate per 1,000")+
  geom_sf_text(data=DEPS,aes(label = Departamento),size=2)+
  theme_map() + ggtitle("Estimation of Age-standardised death rates in 2020")+ 
  theme(panel.background = element_rect(fill = 'white'),legend.position="bottom")

mr2<-ggplot() + geom_sf(data = DEPS,
                       aes(fill=Difference),size=.01,colour="white") +
  scale_fill_viridis_c( direction=1,option = "plasma",
                        name = "Difference per 1,000 deaths")+
  geom_sf_text(data=DEPS,aes(label = Departamento),size=2)+
  theme_map()+ ggtitle("Difference between INEI projections and current estimation")+ 
  theme(panel.background = element_rect(fill = 'white'),legend.position="bottom")

@@

```{r, log, results='asis}

>>>>

\begin{equation}
(\#eq:unreg)
   \begin{aligned}
  \widehat{\mu}_{\text{Deaths}_\text{Not reg}}= \big(1-\widehat{\text{Completeness}}\big)*
  \sum{\widehat{{\text{Excess}}_\text{Reg}}}
   \end{aligned}      
\end{equation}

@@

pander(a, caption = "(\\#tab:summary) Summary of estimations, Peru, 2020.", 
       style = 'rmarkdown', 
       split.table = Inf,
       round=1)

@@

``` {r map2, fig.cap="Age-standardised mortality rates"}

mr1<-ggplot() + geom_sf(data = DEPS,
                       aes(fill=adj.rate),size=.01,colour="white") +
  scale_fill_viridis_c( direction=1,option = "plasma",
                        name = "Age-standardised mortality rate per 1,000")+
  geom_sf_text(data=DEPS,aes(label = Departamento),size=2)+
  theme_map() +
  theme(panel.background = element_rect(fill = 'white'),legend.position="bottom",
        legend.title=element_text(size=7))

mr2<-ggplot() + geom_sf(data = DEPS,
                       aes(fill=Difference),size=.01,colour="white") +
  scale_fill_viridis_c( direction=1,option = "plasma",
                        name = "Difference between INEI's projections and 2020 estimates")+
  geom_sf_text(data=DEPS,aes(label = Departamento),size=2)+
  theme_map()+
  theme(panel.background = element_rect(fill = 'white'),legend.position="bottom",
        legend.title=element_text(size=7))

@@

```{r, log, results='asis'}
